Supplement

### 2023-09-25 paper/supplement.Rmd
add median effect sizes to supp

```{r forest, out.height="100%", fig.width=9, fig.height=12, fig.pos="ht", fig.cap="Forest plot of original and replication effect sizes. Original effect sizes are open dots, replication are closed dots. Coloring indicates subjective replication score, and p-original values are listed on the left side. "}

>>>>

```{r}
# relative effect size

medians <- d %>% filter(include =="stats") %>% summarize(orig=quantile(target_d_calc), rep=quantile(rep_d_calc))

```{r forest, out.height="100%", fig.width=9, fig.height=12, fig.pos="ht", fig.cap="Forest plot of original and replication effect sizes (N=112). Original effect sizes are open dots, replication are closed dots. Coloring indicates subjective replication score, and p-original values are listed on the left side. The median original effect size was .61 and the median replication effect size was .28. "}
